Manuscript draft

### 2019-07-17 manuscript/manuscript draft.Rmd
updated manuscript draft

@@

>>>>

**Mean annual temperature.** All carbon fluxes show a linear increase with temperature.  
**Temperature seasonality and annual temperature range.** These two climate variables are strongly correlated, and so only temperature seasonality is presented in figure 4. Productivity is highest where temperature seasonality = 0, and at an annual temperature range of 15$^\circ$C or lower. GPP, NPP, ANPP, and R~root~ show a polynomial relationship with both variables, and BNPP~root~ shows a polynomial relationship with annual temperature range. As seasonality increases, these variables show a more rapid decrease in productivity. ANPP~foliage~ and ANPP~woodystem~ show a linear relationship with both variables.  
**Mean annual precipitation.** Despite being a poor predictor of productivity, the results indicate that, for the majority of fluxes, productivity increases with precipitation, up until a saturation point at between 3000 and 4000mm annual precipitation, above which productivity starts to decrease. The notable exception to this is GPP, which shows a significant (p<0.0001) linear increase with precipitation up to measures of nearly 6000mm annually, although the explanatory power of this model was low (r-squared = 0.15).  
**Potential evapotranspiration.** All fluxes, with the exception of BNPP~rootfine~ and R~root~ show a strong increase with potential evapotranspiration at values below 1000mm. Between 1200 and 1700mm productivity peaks, and begins to decrease at values above 1800mm.

The best multivariate models explained similar amounts of variation to

@@

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivariate_models <- read.csv("C:/Users/banburymorganr/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/multivariate_models.csv", stringsAsFactors = FALSE, check.names = FALSE)
rownames(multivariate_models) <- c("GPP", "NPP", "ANPP", "ANPP\\textsubscript{foliage}", "ANPP\\textsubscript{woody stem}", "BNPP", "BNPP\\textsubscript{root}", "R\\textsubscript{root}")
kable(multivariate_models, format = "latex", booktabs = TRUE, caption = "Multivariate model output summary. For each carbon flux, correlation coefficients are presented for the two climate variables which explain the most variation when included in a multivariate model. If the model includes an interactive effect, correlation coefficients for the interaction are presented. Results for R\\textsubscript{auto} are not presented here due to the small sample size (n = 14).  ", escape = FALSE, row.names = TRUE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1:10, width = "2cm") %>%
  add_header_above(c(" ", " ", " ", "Correlation coefficients of climate variables" = 6, " "))

```
